Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
Section 3 Keynote: minor changes.

WSSSPE3 broke free of the traditional Supercomputing Conference
environment this year, and in Turk's words, it spoke to the fact that scientific
software comes from many different types of inquiries, deployment, strategies
for maintenance, users; and ways of measuring the value of a piece of software.
It appeared to Turk that the supercomputing conferences generally adopt some
top-down approaches, whereas SciPy bottom-up systems; the essential messages
perceived were also often circumpolar: software getting harder in supercomputing
communities with exascale computing and optimization issues in mind, but software becoming better in the
SciPy groups with emerging tools such as Jupiter and productivity packages for research workflow.
Admitting such comparisons are somewhat unfair generalization, Turk reminded the
audience that the different approaches bring different types of ideas to the
table, but he welcomed that WSSSPE3 was outside existing preconceptions.

>>>>

WSSSPE3 broke free of the traditional Supercomputing Conference
environment this year, and in Turk's words, it spoke to the fact that scientific
software comes from many different types of inquiries, deployment, strategies
for maintenance, users; and ways of measuring the value of a piece of software.
It appeared to Turk that the supercomputing conferences generally adopt some
top-down approaches, whereas SciPy bottom-up systems; the essential messages
perceived were also often circumpolar: software getting harder in supercomputing
communities with exascale computing and optimization issues in mind, but software becoming better in the
SciPy groups with emerging tools such as Jupiter and productivity packages for research workflow.
Admitting such comparisons are somewhat unfair generalization, Turk reminded the
audience that the different approaches bring different types of ideas to the
table, but he welcomed that WSSSPE3 being conducted outside existing preconceptions.
